---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```
## Overview

<!-- badges: start -->
<!-- badges: end -->

User-friendly and flexible algorithm for modeling, sampling, inference, and clustering heteregenous data with the Skew-Normal Mixture-of-Experts (SNMoE) model.

## Installation

You can install the development version of STMoE from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/SNMoE")
```

To build *vignettes* for examples of usage, type the command below instead:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/SNMoE", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         build_vignettes = TRUE)
```

Use the following command to display vignettes:

```{r, eval = FALSE}
browseVignettes("SNMoE")
```

## Usage

```{r, message = FALSE}
library(SNMoE)

data("simulatedstructureddata")

K <- 2 # Number of regimes (mixture components)
p <- 1 # Dimension of beta (order of the polynomial regressors)
q <- 1 # Dimension of w (order of the logistic regression: to be set to 1 for segmentation)

n_tries <- 1
max_iter <- 1500
threshold <- 1e-6
verbose <- TRUE
verbose_IRLS <- FALSE

snmoe <- emSNMoE(simulatedstructureddata$X, matrix(simulatedstructureddata$Y), 
                 K, p, q, n_tries, max_iter, threshold, verbose, verbose_IRLS)

snmoe$plot()
```
