---
output: github_document
bibliography: bibliography.bib
csl: chicago-author-date.csl
nocite: '@*'
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```

<!-- badges: start -->
<!-- badges: end -->

## Overview

Mixtures-of-ExperTs modEling for cOmplex and non-noRmal dIsTributions

MEteoritS is a toolbox containg several original and flexible mixtures-of-experts models to model, cluster and classify heteregenous data in many complex situations where the data are distributed according non-normal, possibly skewed distributions, and when they might be corrupted by atypical observations. The toolbox contains in particular sparse mixture-of-experts models for high-dimensional data. 

Our (dis-)covered meteorites are for instance the following:

* NMoE
* NNMoE
* tMoE
* StMoE 
* SNMoE 
* RMoE

The models and algorithms are developped and written in Matlab by Faicel Chamroukhi, and translated and designed into R packages by Florian Lecocq, Marius Bartcus and Faicel Chamroukhi.

## Installation

You can install the development version of STMoE from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/MEteorits")
```

To build *vignettes* for examples of usage, type the command below instead:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/MEteorits", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         build_vignettes = TRUE)
```

Use the following command to display vignettes:

```{r, eval = FALSE}
browseVignettes("MEteorits")
```

## Usage
<details>
  <summary>SNMoE</summary>
```{r, message = FALSE}
library(meteorits)

data("simulatedstructureddata")

K <- 2 # Number of regimes (mixture components)
p <- 1 # Dimension of beta (order of the polynomial regressors)
q <- 1 # Dimension of w (order of the logistic regression: to be set to 1 for segmentation)

n_tries <- 1
max_iter <- 1500
threshold <- 1e-6
verbose <- TRUE
verbose_IRLS <- FALSE

snmoe <- emSNMoE(simulatedstructureddata$X, matrix(simulatedstructureddata$Y), 
                 K, p, q, n_tries, max_iter, threshold, verbose, verbose_IRLS)

snmoe$plot()
```
</details>

<details>
<summary>StMoE</summary>

```{r, message = FALSE}
library(meteorits)

data("simulatedstructureddata")

K <- 2 # Number of regimes (mixture components)
p <- 1 # Dimension of beta (order of the polynomial regressors)
q <- 1 # Dimension of w (order of the logistic regression: to be set to 1 for segmentation)

n_tries <- 1
max_iter <- 1500
threshold <- 1e-5
verbose <- TRUE
verbose_IRLS <- FALSE

stmoe <- emStMoE(simulatedstructureddata$X, matrix(simulatedstructureddata$Y), 
                 K, p, q, n_tries, max_iter, threshold, verbose, verbose_IRLS)

stmoe$plot()
```
</details>

<details>
<summary>TMoE</summary>
```{r, message = FALSE}
library(meteorits)

data("simulatedstructureddata")

K <- 2 # Number of regimes (mixture components)
p <- 1 # Dimension of beta (order of the polynomial regressors)
q <- 1 # Dimension of w (order of the logistic regression: to be set to 1 for segmentation)

n_tries <- 1
max_iter <- 1500
threshold <- 1e-5
verbose <- TRUE
verbose_IRLS <- FALSE

tmoe <- emTMoE(simulatedstructureddata$X, matrix(simulatedstructureddata$Y), K, p, q, n_tries, max_iter, threshold, verbose, verbose_IRLS)

tmoe$plot()
```

</details>



<details>
<summary>NMoE</summary>
```{r, message = FALSE}
library(meteorits)

data("simulatedstructureddata")

K <- 2 # Number of regimes (mixture components)
p <- 1 # Dimension of beta (order of the polynomial regressors)
q <- 1 # Dimension of w (order of the logistic regression: to be set to 1 for segmentation)

n_tries <- 1
max_iter <- 1500
threshold <- 1e-5
verbose <- TRUE
verbose_IRLS <- FALSE

nmoe <- emNMoE(simulatedstructureddata$X, matrix(simulatedstructureddata$Y), K, p, q, n_tries, max_iter, threshold, verbose, verbose_IRLS)

nmoe$plot()
```

</details>

# References

