---
output: github_document
bibliography: bibliography.bib
csl: chicago-author-date.csl
nocite: '@*'
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```

# **MEteorits:** Mixtures-of-ExperTs modEling for cOmplex and non-noRmal dIsTributions

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/fchamroukhi/MEteorits.svg?branch=master)](https://travis-ci.org/fchamroukhi/MEteorits)
[![CRAN versions](https://www.r-pkg.org/badges/version/meteorits)](https://cran.r-project.org/web/packages/meteorits/index.html)
<!-- badges: end -->

MEteorits is an open source toolbox (available in R and Matlab) containing 
several original and flexible mixtures-of-experts models to model, cluster and
classify heteregenous data in many complex situations where the data are 
distributed according to non-normal and possibly skewed distributions, and 
when they might be corrupted by atypical observations. The toolbox also 
contains sparse mixture-of-experts models for high-dimensional data.

Our (dis-)covered meteorits are for instance the following ones:

* NMoE (Normal Mixtures-of-Experts);
* tMoE (t Mixtures-of-Experts);
* SNMoE (Skew-Normal Mixtures-of-Experts);
* StMoE (Skew t Mixtures-of-Experts).

The models and algorithms are developped and written in Matlab by Faicel 
Chamroukhi, and translated and designed into R packages by Florian Lecocq, 
Marius Bartcus and Faicel Chamroukhi.

# Installation

You can install the development version of MEteorits from [GitHub](https://github.com/fchamroukhi/MEteorits) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/MEteorits")
```

To build *vignettes* for examples of usage, type the command below instead:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/MEteorits", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         build_vignettes = TRUE)
```

Use the following command to display vignettes:

```{r, eval = FALSE}
browseVignettes("meteorits")
```

# Usage

```{r, message = FALSE}
library(meteorits)
```

<details>
  <summary>NMoE</summary>

```{r, echo = TRUE}
# Application to a simulated data set

n <- 500 # Size of the sample
alphak <- matrix(c(0, 8), ncol = 1) # Parameters of the gating network
betak <- matrix(c(0, -2.5, 0, 2.5), ncol = 2) # Regression coefficients of the experts
sigmak <- c(1, 1) # Standard deviations of the experts
x <- seq.int(from = -1, to = 1, length.out = n) # Inputs (predictors)

# Generate sample of size n
sample <- sampleUnivNMoE(alphak = alphak, betak = betak, 
                         sigmak = sigmak, x = x)
y <- sample$y

K <- 2 # Number of regressors/experts
p <- 1 # Order of the polynomial regression (regressors/experts)
q <- 1 # Order of the logistic regression (gating network)

nmoe <- emNMoE(X = x, Y = y, K = K, p = p, q = q, verbose = TRUE)

nmoe$summary()

nmoe$plot()
```

```{r, echo = TRUE}
# Application to a real data set

data("tempanomalies")
x <- tempanomalies$Year
y <- tempanomalies$AnnualAnomaly

K <- 2 # Number of regressors/experts
p <- 1 # Order of the polynomial regression (regressors/experts)
q <- 1 # Order of the logistic regression (gating network)

nmoe <- emNMoE(X = x, Y = y, K = K, p = p, q = q, verbose = TRUE)

nmoe$summary()

nmoe$plot()
```
</details>

<details>

  <summary>TMoE</summary>

```{r, echo = TRUE}
# Application to a simulated data set

n <- 500 # Size of the sample
alphak <- matrix(c(0, 8), ncol = 1) # Parameters of the gating network
betak <- matrix(c(0, -2.5, 0, 2.5), ncol = 2) # Regression coefficients of the experts
sigmak <- c(0.5, 0.5) # Standard deviations of the experts
nuk <- c(5, 7) # Degrees of freedom of the experts network t densities
x <- seq.int(from = -1, to = 1, length.out = n) # Inputs (predictors)

# Generate sample of size n
sample <- sampleUnivTMoE(alphak = alphak, betak = betak, sigmak = sigmak, 
                         nuk = nuk, x = x)
y <- sample$y

K <- 2 # Number of regressors/experts
p <- 1 # Order of the polynomial regression (regressors/experts)
q <- 1 # Order of the logistic regression (gating network)

tmoe <- emTMoE(X = x, Y = y, K = K, p = p, q = q, verbose = TRUE)

tmoe$summary()

tmoe$plot()
```

```{r, echo = TRUE}
# Application to a real data set

library(MASS)
data("mcycle")
x <- mcycle$times
y <- mcycle$accel

K <- 4 # Number of regressors/experts
p <- 2 # Order of the polynomial regression (regressors/experts)
q <- 1 # Order of the logistic regression (gating network)

tmoe <- emTMoE(X = x, Y = y, K = K, p = p, q = q, verbose = TRUE)

tmoe$summary()

tmoe$plot()
```
</details>

<details>
  <summary>SNMoE</summary>

```{r, echo = TRUE}
# Application to a simulated data set

n <- 500 # Size of the sample
alphak <- matrix(c(0, 8), ncol = 1) # Parameters of the gating network
betak <- matrix(c(0, -2.5, 0, 2.5), ncol = 2) # Regression coefficients of the experts
lambdak <- c(3, 5) # Skewness parameters of the experts
sigmak <- c(1, 1) # Standard deviations of the experts
x <- seq.int(from = -1, to = 1, length.out = n) # Inputs (predictors)

# Generate sample of size n
sample <- sampleUnivSNMoE(alphak = alphak, betak = betak, 
                          sigmak = sigmak, lambdak = lambdak, 
                          x = x)
y <- sample$y

K <- 2 # Number of regressors/experts
p <- 1 # Order of the polynomial regression (regressors/experts)
q <- 1 # Order of the logistic regression (gating network)

snmoe <- emSNMoE(X = x, Y = y, K = K, p = p, q = q, verbose = TRUE)

snmoe$summary()

snmoe$plot()
```

```{r, echo = TRUE}
# Application to a real data set

data("tempanomalies")
x <- tempanomalies$Year
y <- tempanomalies$AnnualAnomaly

K <- 2 # Number of regressors/experts
p <- 1 # Order of the polynomial regression (regressors/experts)
q <- 1 # Order of the logistic regression (gating network)

snmoe <- emSNMoE(X = x, Y = y, K = K, p = p, q = q, verbose = TRUE)

snmoe$summary()

snmoe$plot()
```
</details>

<details>
  <summary>StMoE</summary>

```{r, echo = TRUE}
# Applicartion to a simulated data set

n <- 500 # Size of the sample
alphak <- matrix(c(0, 8), ncol = 1) # Parameters of the gating network
betak <- matrix(c(0, -2.5, 0, 2.5), ncol = 2) # Regression coefficients of the experts
sigmak <- c(0.5, 0.5) # Standard deviations of the experts
lambdak <- c(3, 5) # Skewness parameters of the experts
nuk <- c(5, 7) # Degrees of freedom of the experts network t densities
x <- seq.int(from = -1, to = 1, length.out = n) # Inputs (predictors)

# Generate sample of size n
sample <- sampleUnivStMoE(alphak = alphak, betak = betak, 
                          sigmak = sigmak, lambdak = lambdak, 
                          nuk = nuk, x = x)
y <- sample$y

K <- 2 # Number of regressors/experts
p <- 1 # Order of the polynomial regression (regressors/experts)
q <- 1 # Order of the logistic regression (gating network)

stmoe <- emStMoE(X = x, Y = y, K = K, p = p, q = q, verbose = TRUE)

stmoe$summary()

stmoe$plot()
```

```{r, echo = TRUE}
# Applicartion to a real data set

library(MASS)
data("mcycle")
x <- mcycle$times
y <- mcycle$accel

K <- 4 # Number of regressors/experts
p <- 2 # Order of the polynomial regression (regressors/experts)
q <- 1 # Order of the logistic regression (gating network)

stmoe <- emStMoE(X = x, Y = y, K = K, p = p, q = q, verbose = TRUE)

stmoe$summary()

stmoe$plot()
```
</details>

# References
