---
title: "A-quick-tour-of-StMoE"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A-quick-tour-of-StMoE}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
	fig.align = "center",
	fig.height = 5.5,
	fig.width = 6,
	warning = FALSE,
	collapse = TRUE,
	dev.args = list(pointsize = 10),
	out.width = "90%",
	par = TRUE
)
knit_hooks$set(par = function(before, options, envir)
  { if (before && options$fig.show != "none") 
       par(family = "sans", mar = c(4.1,4.1,1.1,1.1), mgp = c(3,1,0), tcl = -0.5)
})
```

```{r, message = FALSE, echo = FALSE}
library(meteorits)
```

# Introduction

**MEteorit** is a toolbox containg several original and flexible mixtures-of-experts models to model, cluster and classify heteregenous data in many complex situations where the data are distributed according non-normal, possibly skewed distributions, and when they might be corrupted by atypical observations. The toolbox contains in particular sparse mixture-of-experts models for high-dimensional data. 
It was written in R Markdown, using the [knitr](https://cran.r-project.org/package=knitr) package for production. 
See `help(package="meteorit")` for further details and references provided by `citation("meteorit")`.

# Load data

```{r}
data("simulatedstructureddata")
```

# Set up StMoE model parameters

```{r}
K <- 2 # Number of regimes (mixture components)
p <- 1 # Dimension of beta (order of the polynomial regressors)
q <- 1 # Dimension of w (order of the logistic regression: to be set to 1 for segmentation)

```

# Set up EM parameters

```{r}
n_tries <- 1
max_iter <- 1500
threshold <- 1e-5
verbose <- TRUE
verbose_IRLS <- FALSE
```

# Estimation

```{r}
stmoe <- emStMoE(simulatedstructureddata$X, matrix(simulatedstructureddata$Y), K, p, q, n_tries, max_iter, threshold, verbose, verbose_IRLS)
```

# Plots

## Mean curve

```{r}
stmoe$plot(what = "meancurve")
```

## Confidence regions

```{r}
stmoe$plot(what = "confregions")
```

## Clusters

```{r}
stmoe$plot(what = "clusters")
```

## Log-likelihood

```{r}
stmoe$plot(what = "loglikelihood")
```
