---
title: "A-quick-tour-of-StMoE"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A-quick-tour-of-StMoE}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
	fig.align = "center",
	fig.height = 5.5,
	fig.width = 6,
	warning = FALSE,
	collapse = TRUE,
	dev.args = list(pointsize = 10),
	out.width = "90%",
	par = TRUE
)
knit_hooks$set(par = function(before, options, envir)
  { if (before && options$fig.show != "none") 
       par(family = "sans", mar = c(4.1,4.1,1.1,1.1), mgp = c(3,1,0), tcl = -0.5)
})
```

```{r, message = FALSE, echo = FALSE}
library(meteorits)
```

# Introduction

**MEteorit** is a toolbox containg several original and flexible 
mixtures-of-experts models to model, cluster and classify heteregenous data in 
many complex situations where the data are distributed according non-normal, 
possibly skewed distributions, and when they might be corrupted by atypical
observations. The toolbox contains in particular sparse mixture-of-experts 
models for high-dimensional data. 

It was written in R Markdown, using the [knitr](https://cran.r-project.org/package=knitr) 
package for production.

See `help(package="meteorits")` for further details and references provided by
`citation("meteorits")`.

# Application to a simulated dataset

## Generate sample

```{r}
n <- 500 # Size of the sample
alphak <- matrix(c(0, 8), ncol = 1) # Parameters of the gating network
betak <- matrix(c(0, -2.5, 0, 2.5), ncol = 2) # Regression coefficients of the experts
sigmak <- c(0.5, 0.5) # Standard deviations of the experts
lambdak <- c(3, 5) # Skewness parameters of the experts
nuk <- c(5, 7) # Degrees of freedom of the experts network t densities
x <- seq.int(from = -1, to = 1, length.out = n) # Inputs (predictors)

# Generate sample of size n
sample <- sampleUnivSTMoE(alphak = alphak, betak = betak, sigmak = sigmak, 
                          lambdak = lambdak, nuk = nuk, x = x)
```

## Set up StMoE model parameters

```{r}
K <- 2 # Number of regressors/experts
p <- 1 # Order of the polynomial regression (regressors/experts)
q <- 1 # Order of the logistic regression (gating network)
```

## Set up EM parameters

```{r}
n_tries <- 1
max_iter <- 1500
threshold <- 1e-5
verbose <- TRUE
verbose_IRLS <- FALSE
```

## Estimation

```{r}
stmoe <- emStMoE(x, matrix(sample$y), K, p, q, n_tries, max_iter, 
                 threshold, verbose, verbose_IRLS)
```

## Plots

### Mean curve

```{r}
stmoe$plot(what = "meancurve")
```

### Confidence regions

```{r}
stmoe$plot(what = "confregions")
```

### Clusters

```{r}
stmoe$plot(what = "clusters")
```

### Log-likelihood

```{r}
stmoe$plot(what = "loglikelihood")
```

# Application to real dataset

## Load data

```{r}
library(MASS)
data("mcycle")
x <- mcycle$times
y <- as.matrix(mcycle$accel)
```

## Set up StMoE model parameters

```{r}
K <- 4 # Number of regressors/experts
p <- 2 # Order of the polynomial regression (regressors/experts)
q <- 1 # Order of the logistic regression (gating network)
```

## Set up EM parameters

```{r}
n_tries <- 1
max_iter <- 1500
threshold <- 1e-5
verbose <- TRUE
verbose_IRLS <- FALSE
```

## Estimation

```{r}
stmoe <- emStMoE(X = x, Y = y, K, p, q, n_tries, max_iter, 
                 threshold, verbose, verbose_IRLS)
```

## Plots

### Mean curve

```{r}
stmoe$plot(what = "meancurve")
```

### Confidence regions

```{r}
stmoe$plot(what = "confregions")
```

### Clusters

```{r}
stmoe$plot(what = "clusters")
```

### Log-likelihood

```{r}
stmoe$plot(what = "loglikelihood")
```
